Scikit-learn: machine learning without learning the machinery

### 2014-05-18 article.tex
Wording

\begin{abstract}
Machine learning is a pervasive development at the intersection of
statistics and computer science. While it could benefit to many
data-related applications, the technicality of the research literature
and the corresponding algorithms slows down its adoption. Scikit-learn is
a open-source software project that aims to make machine learning
accessible to all, whether it be in academia or in the industry. It
fosters the general-purpose Python language, that enjoys a huge growth in
the scientific world, and well as a striving ecosystem of contributors.
Here we give a quick introduction to the scikit-learn as well as to
machine-learning basics.
\end{abstract}

>>>>

\begin{abstract}
Machine learning is a pervasive development at the intersection of
statistics and computer science. While it can benefit many
data-related applications, the technicality of the research literature
and the corresponding algorithms slows down its adoption. Scikit-learn is
a open-source software project that aims to make machine learning
accessible to all, whether it be in academia or in the industry. It
fosters the general-purpose Python language, that enjoys a huge growth in
the scientific world, and well as a striving ecosystem of contributors.
Here we give a quick introduction to the scikit-learn as well as to
machine-learning basics.
\end{abstract}
